When does vapor pressure deficit drive or reduce evapotranspiration?

### 2019-06-19 doc/paper/agu-james-submission.tex
james submission compiles, need to proof read and encorporate with makefile
added key points

%% To submit your paper:
\documentclass[draft]{agujournal2019}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
% \usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
\usepackage{soul}
\linenumbers

@@

\begin{keypoints}
\item enter point 1 here
\item enter point 2 here
\item enter point 3 here
\end{keypoints}

>>>>

%% To submit your paper:
\documentclass[draft]{agujournal2019}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
% \usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
\usepackage{soul}

%% added by adam
\usepackage{amsmath}
\usepackage{amssymb}
\newcommand{\appropto}{\mathrel{\vcenter{
      \offinterlineskip\halign{\hfil$##$\cr
        \propto\cr\noalign{\kern2pt}\sim\cr\noalign{\kern-2pt}}}}}

\linenumbers

@@

\begin{keypoints}
\item Using Penman-Monteith, a semi-empirical stomatal conductance
  model, and underlying water use efficiency, we develop a simplified
  analytical theory for when ecosystems will reduce or increase
  evapotranspiration in response to vapor pressure deficit perturbations.
\item The observed range of plant parameters result in a broad range
  of ecosystem response to increases in vapor pressure deficit, from
  strong reductions in evapotranspiration to strong increases in
  evapotranspiration depending on ecosystem type and environment.
\item The choice of stomatal conductance model fundamentally alters
  the relationship between evapotranspiration and vapor pressure
  deficit, highlighting the need for further research on stomatal
  conductance and its representation in more sophisticated land
  surface models.
\end{keypoints}
